### 2024-08-08 NN/plots_latex.tex
zz

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Relu2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-20.png}
    \caption{Relu2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Relu2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-12.png}
    \caption{Relu2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/FFNN-R2-vs-Num-of-Epochs-HiddenSize-20.png}
    \caption{FFNN - R2 vs. Number of Epochs (Hidden Size: 20)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/FFNN-R2-vs-Num-of-Epochs-HiddenSize-28.png}
    \caption{FFNN - R2 vs. Number of Epochs (Hidden Size: 28)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/FFNN-R2-vs-Num-of-Epochs-HiddenSize-12.png}
    \caption{FFNN - R2 vs. Number of Epochs (Hidden Size: 12)}
\end{figure}

>>>>

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Tanh1HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-10.png}
    \caption{Tanh1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 10)}
\end{figure}

### 2024-08-08 NN/plots_preds_latex.tex
commit
zz

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots_preds/R2-99.65-GRNN-Impedance module.png}
    \caption{Prediction of Impedance module with GRNN - R-Squared: 0.97}
\end{figure}

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots_preds/R2-93.87-Tanh2HiddenLayer-Impedance-module.png}
    \caption{Prediction of Impedance module with Tanh2HiddenLayer - R-Squared: 0.94}
\end{figure}

### 2024-08-08 NN/tables/backward.tex
commit
zz

    \begin{table*}
        \centering
        \begin{tabular}{p{12cm}r}r}
\hline
\hline
 features                                                                                            &    R2 \\
\hline
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2 & 84.97 \\
 conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 71.27 \\
 flow\_rate1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 71.9  \\
 flow\_rate1,conc\_nano1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2         & 73.44 \\
 flow\_rate1,conc\_nano1,Kfluid1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 74.25 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2       & 70.58 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 81.67 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,Kfluid2,heat\_flux2,X\_D2             & 40.24 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,heat\_flux2,X\_D2         & 49.33 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,X\_D2             & 72.42 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2       & 74.5  \\
\hline
\end{tabular}
\hline
        \caption{Results of Backward Feature Elimination}
        \label{backward}
    \end{table*}

>>>>

    \begin{table*}[h]
        \centering
        \begin{tabular}{lr}
\hline
 features                                                                                                                                 &    R2 \\
\hline
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp & 77.62 \\
 Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp             & 51.9  \\
 SG Coating, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp               & 51.9  \\
 SG Coating, Temp Alk Sol, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp            & 51.9  \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp                     & 74.59 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp         & 46.26 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp                 & 69.37 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Clay Conc, Cure Time (min), Cure Temp                   & 62.26 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Cure Time (min), Cure Temp            & 34.36 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Temp                  & 64.92 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min)            & 62.82 \\
\hline
\end{tabular}
        \caption{Results of Backward Feature Elimination}
        \label{backward}
    \end{table*}

### 2024-08-08 NN/tables/forward.tex
zz

    \begin{table*}
        \centering
        \begin{tabular}{lr}
\hline
 features                                                      &    R2 \\
\hline
 X\_D1                                                         & 15.01 \\
 flow\_rate2                                                   & 34.3  \\
 conc\_nano2                                                   & 10.78 \\
 Kfluid2                                                       & 49.29 \\
 heat\_flux2                                                   & -8.26 \\
 flow\_rate1,Kfluid2                                           & 52.94 \\
 conc\_nano1,Kfluid2                                           & 50.8  \\
 Kfluid1,Kfluid2                                               & 47.57 \\
 heat\_flux1,Kfluid2                                           & 52.31 \\
 X\_D1,Kfluid2                                                 & 62.32 \\
 flow\_rate2,Kfluid2                                           & 29.14 \\
 conc\_nano2,Kfluid2                                           & 61.05 \\
 heat\_flux2,Kfluid2                                           & 66.61 \\
 X\_D2,Kfluid2                                                 & 53.44 \\
 flow\_rate1,Kfluid2,heat\_flux2                               & 60.58 \\
 conc\_nano1,Kfluid2,heat\_flux2                               & 61.96 \\
 Kfluid1,Kfluid2,heat\_flux2                                   & 66.64 \\
 heat\_flux1,Kfluid2,heat\_flux2                               & 42.41 \\
 X\_D1,Kfluid2,heat\_flux2                                     & 66.55 \\
 flow\_rate2,Kfluid2,heat\_flux2                               & 55.24 \\
 conc\_nano2,Kfluid2,heat\_flux2                               & 67.09 \\
 X\_D2,Kfluid2,heat\_flux2                                     & 68.58 \\
 flow\_rate1,Kfluid2,heat\_flux2,X\_D2                         & 90.12 \\
 conc\_nano1,Kfluid2,heat\_flux2,X\_D2                         & 78.64 \\
 Kfluid1,Kfluid2,heat\_flux2,X\_D2                             & 88.23 \\
 heat\_flux1,Kfluid2,heat\_flux2,X\_D2                         & 49.47 \\
 X\_D1,Kfluid2,heat\_flux2,X\_D2                               & 79.9  \\
 flow\_rate2,Kfluid2,heat\_flux2,X\_D2                         & -0.88 \\
 conc\_nano2,Kfluid2,heat\_flux2,X\_D2                         & 63.17 \\
 conc\_nano1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1             & 95.97 \\
 Kfluid1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1                 & 76.54 \\
 heat\_flux1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1             & 60.12 \\
 X\_D1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1                   & 80.67 \\
 flow\_rate2,Kfluid2,heat\_flux2,X\_D2,flow\_rate1             & 68.87 \\
 conc\_nano2,Kfluid2,heat\_flux2,X\_D2,flow\_rate1             & 68.35 \\
 Kfluid1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1,conc\_nano1     & 80.62 \\
 heat\_flux1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1,conc\_nano1 & 67.03 \\
 X\_D1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1,conc\_nano1       & 85.73 \\
 flow\_rate2,Kfluid2,heat\_flux2,X\_D2,flow\_rate1,conc\_nano1 & 75.7  \\
 conc\_nano2,Kfluid2,heat\_flux2,X\_D2,flow\_rate1,conc\_nano1 & 78.99 \\
\hline
\end{tabular}
        \caption{Results of Forward Feature Selection for different features}
        \label{forward}
    \end{table*}

>>>>

    \begin{table*}[h]
        \centering
        \begin{tabular}{lr}
\hline
 features                                                         &     R2 \\
\hline
 pH Sol                                                           &  14.56 \\
 Hydro Time (h)                                                   &  26.4  \\
 Dip Time Sol (s)                                                 &  11.24 \\
 Clay Conc                                                        &  64.24 \\
 Cure Time (min)                                                  &   0.1  \\
 SG Coating, Clay Conc                                            &  64.93 \\
 Temp Alk Sol, Clay Conc                                          &  64.93 \\
 NaOH Wt\%, Clay Conc                                             &  64.93 \\
 Dip Time Alk (min), Clay Conc                                    &  79.07 \\
 pH Sol, Clay Conc                                                &  62.87 \\
 Hydro Time (h), Clay Conc                                        & -15.61 \\
 Dip Time Sol (s), Clay Conc                                      &  80.99 \\
 Cure Time (min), Clay Conc                                       &  74.1  \\
 Cure Temp, Clay Conc                                             &  66.68 \\
 SG Coating, Clay Conc, Dip Time Sol (s)                          &  81.03 \\
 Temp Alk Sol, Clay Conc, Dip Time Sol (s)                        &  81.03 \\
 NaOH Wt\%, Clay Conc, Dip Time Sol (s)                           &  81.03 \\
 Dip Time Alk (min), Clay Conc, Dip Time Sol (s)                  &  93.94 \\
 pH Sol, Clay Conc, Dip Time Sol (s)                              &  83.22 \\
 Hydro Time (h), Clay Conc, Dip Time Sol (s)                      &  56.92 \\
 Cure Time (min), Clay Conc, Dip Time Sol (s)                     &  60.09 \\
 Cure Temp, Clay Conc, Dip Time Sol (s)                           &  60.67 \\
 SG Coating, Clay Conc, Dip Time Sol (s), Dip Time Alk (min)      &  85.55 \\
 Temp Alk Sol, Clay Conc, Dip Time Sol (s), Dip Time Alk (min)    &  85.55 \\
 NaOH Wt\%, Clay Conc, Dip Time Sol (s), Dip Time Alk (min)       &  85.55 \\
 pH Sol, Clay Conc, Dip Time Sol (s), Dip Time Alk (min)          &  77.04 \\
 Hydro Time (h), Clay Conc, Dip Time Sol (s), Dip Time Alk (min)  &  75.85 \\
 Cure Time (min), Clay Conc, Dip Time Sol (s), Dip Time Alk (min) &  71.81 \\
 Cure Temp, Clay Conc, Dip Time Sol (s), Dip Time Alk (min)       &  63.33 \\
\hline
\end{tabular}
        \caption{Results of Forward Feature Selection for different features}
        \label{forward}
    \end{table*}
